\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\newline


\textbf{Cloud computing} is a pay-per-use model that enables available, convenient, on-demand network access to a shared pool of configurable computing resources (e.g., networks, servers, storage, applications, services) that can be rapidly provisioned and released with minimal management effort or interaction from service providers. This cloud model promotes availability and includes five key features, three delivery models, and four deployment models. Other leading cloud models, such as Microsoft Azure, Amazon Web Services, Google Cloud Platform & Salesforce.
I gathered some of the best quotes from the world of cloud computing and highly recommend you read them @ \href{https://devops.yahya-abulhaj.dev/}{DevOps.yahya-abulhaj.dev/}. 
\newline \newline
\newline \textbf{Entreprise Information:}\newline 
\textbf{Linedata} is a global publisher of value-added software, services, and data for the financial industry. Linedata has been assisting its clients, asset managers, institutional and alternative fund managers, fund administrators, and credit and financing institutions, in meeting their challenges for over 20 years through innovative and efficient solutions.
In today's world, quality is the buzzword, and without it, no organization can survive. Along with quality, we at Linedata. "Think Beyond" to go one step further and focus on solution delivery. We design processes that prioritize not only quality but also delivery, increasing the value to our global clients. I did not only get trained  on the latest technologies, but we the team we empower them to provide exciting solutions to our clients.
\newline \newline
\newline \textbf{Program And Opportunities:}\newline 
Linedata's success, in my opinion, is dependent on innovation and creativity. Currently navigating great fields of technology and will continue to do so.\newline 
\textbf{Software}, We create modular software platforms that are cloud-based and highly scalable due to the continuous delivery of new functionalities and modules, and I played a significant role in this.\newline 
\textbf{Analytics and data}, our AI and ML-powered data management services enable our customers to structure and exploit the right data from multiple sources without redundancy or additional cost.\newline 
\textbf{Services}, in key operational functions, our highly skilled experts supplement our clients' teams, delivering results, resilience, scalability, and efficiency.


