

\chapter*{Acknowledgment}
\addcontentsline{toc}{chapter}{Acknowledgment}
\newline

\textbf{Foremost}, I would like to express my sincere gratitude to my mentor Prof. Amal Dridi for the continuous support of my internship, for her patience, motivation, enthusiasm, and immense knowledge. \newline Her guidance helped me in all the time of expermimenting with the latest technologies and contributing to the company.
I could not have imagined having a better advisor and mentor for my summer internship.
\newline
It was a great privilege and honor to work and study under her guidance. I am extremely
grateful for what she has offered me. I would also like to thank her for the
friendship, empathy, and great sense of humor. 
\newline
I am overhelmed in all humbleness and gratefulness to acknowledge my depth to all those who have helped me to put these ideas, well above the level of simplicity and into something concrete.
\newline

Besides my advisor, I would like to thank the rest of the team at the Quality Assurance office: my manager, Marwan Sallem, Mohja Ben Amara for their encouragement, insightful comments, and hard questions.\newline
My sincere thanks also goes to Sandeep repswal, Sanjay Kulkarni from the india office for offering and enrolling me in their work and leading me to contribute on diverse exciting projects.
\newline

I would like to thank my mother who helped me a lot in gathering different information, collecting data and guiding me from time to time in making this state of mind and who i am. I am extremely grateful to her for her love, prayers, caring and
sacrifices for educating and preparing me for my future.
\newline

Also I express my thanks to my sister,
brother for their support and valuable prayers. My
Special thanks goes to my friend Kandarp, my online teammate for the
keen interest shown in career growth and collaboration to achieve success in life.
\newline
\textbf{Thank you, all.}
\vskip1.5cm
\begin{flushright}\LARGE
\bf{Yahya Abulhaj}
\end{flushright}
