\chapter{The Experience}
    %\addcontentsline{toc}{chapter}{}

\section{Internship Introduction}
Cloud computing is a developing technology that has the potential to disrupt traditional IT systems. Cloud computing enables an organization's IT to be more flexible, save money, and process information and data more quickly than traditional IT. The issue, however, is the riskiness of this new technology.

Cloud computing is a new paradigm for hosting and delivering services over the Internet that has recently emerged. Cloud computing is appealing to business owners because it eliminates the need for users to plan ahead for provisioning and allows enterprises to start small and scale up only when service demand increases. Despite the fact that cloud computing provides enormous opportunities for the IT industry, cloud computing technology is still in its infancy, with many issues yet to be addressed.
\newline

Cloud computing has received a lot of attention in the current IT world. After the internet, cloud computing is said to be the next big thing in the computer world. Cloud computing is the use of the Internet for computer tasks, and it is envisioned as the next generation of IT architecture [1].

\section{Motivation}

I was a TECH fanatic. At the end of my first year of college, I discovered my passion for Microsoft Azure and began taking my first online class after another, as well as reading as many related articles as I could. My first cloud computing exam, the AZ-900, Azure Fundamentals, went well. The achievement had a significant impact on my life. And as time went on, I realized how potent this is. Despite the fact that I had no prior technical experience, this exam provided an excellent overview of everything related to Microsoft's vision and discussed the future of cloud computing. The most important points are as follows:

\textbf{Scalability} - Cloud computing is a highly scalable technology. We can use scalability to scale up and down our cloud resources. A cloud-based IT infrastructure is more versatile than a local, intranet-based infrastructure, particularly in terms of scalability.

\textbf{Reliability} - Cloud computing service providers offer consistent and dependable resources. They guarantee uptime of up to 99.99percent. They duplicate our resources and data and distribute them across multiple regions.

\textbf{Virtualization} - Because cloud-based IT infrastructure can be virtualized dislocated, startups are no longer required to consider the physical location of their IT infrastructure and data centers when making business decisions.

\textbf{Affordability} - Under traditional infrastructures, startups may not receive - or have the financial means to purchase - certain features that are frequently offered at substantial discounts to cloud computing customers. How do these advantages trickle down to startups and other small businesses? Because the marginal cost of many features (such as enhanced security) to the cloud computing provider may be very low (or even negligible), otherwise unaffordable services may be offered for free to startups using cloud computing options.

I wrote some of the great foundational cloud knowledge with the use of Microsoft Azure, you can consult it @  \href{https://cloud.itzyahya.tech/A-AZ900}{https://cloud.itzyahya.tech/A-AZ900}.  

\section{Internship Objectives }
The primary goal of this internship is to gain practical knowledge of cloud services and DevOps tools. Moreover, the main focus is on developing a highly available, cost-effective, fault-tolerant, scalable system and working on migrating on-premise infrastructure to the cloud. I had a great time discussing and applying the topics I'm most passionate about with colleagues from India and the United States. It felt great.
\item \textbf{1:} Core services of Amazon Web Services (AWS): IAM, VPC, S3, EC2, SNS..
\item  \textbf{2:} Hands-on DevOps tools and technologies: Terraform, Ansible, Docker, Kubernetes..
\item  \textbf{3:} Gain the communication skill. I consider that a critical one.



\section{Report Layout}

\textbf{Chapter - 1} Describe the internship's introduction, motivation and, objectives.\newline
\textbf{Chapter - 2} Describe the daily tasks, technologies and
activites i worked with.\newline
\textbf{Chapter - 3}  Describe part of the hands-on experience i had at the internship\newline
\textbf{Chapter - 4}  Describe the knowledge I gained and my career goals\newline


