\chapter{Expertise and Clever Strategy}


\section{Expertise Earned}
  During this internship, I learned a variety of new skills that will be useful in my future career.
\begin{itemize}
  \item Apply Cloud Knowledge: AWS.
  \item How to create valuable software
  \item Capability in project management.
  \item Server installation and upkeep Automation of the system.
  \item Taking backup of Important filesystems.
  \item Cybersecurity
  \item Tools and technologies for DevOps
  

\end{itemize}

\section{Clever Strategy}

Cloud computing is expanding at a breakneck pace, and as a result, employer demand for cloud professionals has skyrocketed. I discovered the cloud, and it noticed me.
Someone once said, "The hardest part is getting started; once you do, you become unstoppable," and this is so true. I'm keeping the momentum going, and my goal for the rest of the year is to pass the certification exams listed below.

\begin{itemize}
  \item SC-100: Microsoft Cybersecurity Architect Expert.
  \item Google Cloud Platform: Associate Cloud Engineer.
  \item MS-720: Microsoft Teams Voice Engineer.
  \item AWS Solutions Architect Associate.
\end{itemize}

\section{Reflections}
\textbf{Where did you work? What was your position}\newline
I was assigned the cloud migration topic for the project of my internship at Linedata. I can say that I did well, and that I got into the motion faster than people who had been enrolled for months.
\newline

\textbf{What advice would you give to someone in your field?}\newline
You must be able to adapt to ever-changing technologies in this field. Because new cloud services are released every since. You must be patient. Take your time and continue to learn. The key is perseverance. You will figure out the work smartly the moment you reach that discipline.\newline

\textbf{What did you struggle with throughout your internship?}\newline
Transportation and a lack of funds, to be honest. I'm still perplexed with Tunisians companies, if they greet and welcomes you. It's your best bet. You must focus on learning if this is your best option. It's all that matters, right? However, we must consider compensating people for their efforts.
\newline

\textbf{Why did you leave linedata when you could have spent the entire summer there?}\newline
Right, I was welcome to stay as long as I needed for my internship. But I was faster, and I came across another opportunity on the other side.
\newline

\textbf{What tools did you use or learned to use?}\newline
A plethora of cloud services, devops tools, and server-side scripting.
\newline

\textbf{What you think about your Future?}\newline
As an educated individual who is responsible for myself and my family, I give considerable thought to my future career. Not only me, but any person living in a civilized community thinks about his or her future. 
\newline

\textbf{What you think about success, Are you doing it?}\newline
What I can tell you is that I can see success, but I haven't arrived yet. I'd like to define success in this simple mathematical formula for myself.
Success= Wealth + Health + Time. Additionally, I don't want to enjoy my life when I retire and run out of time. My ambition for the next 5-10 years is to create the formula.