\chapter{TASK PROJECTS AND ACTIVITIES}


\section{Daily Tasks and Activities}
\begin{itemize}
  \item Regularly Monitoring and capturing system log files.
  \item Regularly Monitoring and capturing data of server CPU, memory usage
  \item Regularly monitoring Filesystems space.
  \item Regularly monitoring capturing Network usage.
  \item Taking backup of Important filesystems.
  \item Maintaining documentation.
  \item Hands-on Labs with DevOps technologies.
  \item Contributions to the internal Linedata Repository.

\end{itemize}

\section{Events}
 Meetings with international colleagues and sharing experiences were among the highlights of my trip. I remember every single thing that matters.
Other than that, our organization hasn't held any significant events since I started working for Linedata. However, there were occasions when our QA team members were really busy because our customer assigned some extra work that wasn't related to our project.



\section{Technologies Assigned}
IT is challenging work, as my first intern predicted. I had fun extending my work ethics with several awesome technologies. I'll list below the critical technologies that help me succeed and achieve my goals.

\subsection{Microsoft Azure}
Linedata did not work with Microsoft Azure when I first joined, but that is not an excuse for not mentioning it in this report. Because of such a cloud provider, I am now able to interact with the other 2 cloud provider leaders as AWS and GCP, or any ready-to-configure user interface using the analogy. I still prefer Azure because it allows for easy mobility and a consistent platform between on-premise and public cloud environments. To improve usability and performance, Azure offers a broader range of hybrid connections such as virtual private networks (VPNs), caches, content delivery networks (CDNs), and ExpressRoute connections. I'm aware that these are the same in any other cloud, except with different branding. However, Microsoft has the leading enterprise suite, M365. Recognize the eco-system.
\subsubsection{Touchpoint}
In terms of technology, all clouds are extremely similar. As a result, if you have a solid foundation with one. You're all set. That's correct. I was able to experiment and pass exams from both azure and aws today, 10/06/2022, as well as going for GCP by the end of this year. I'm already stuffed with labs and ready to win.
\subsection{Amazon Web Services}

I joined linedata with 10 microsoft certifications Azure-Focused, but hearing that I'd be dealing with AWS was \textbf{huge}. After completing so much work on a single cloud, it is now time for me to expand that with the world's number one cloud provider. Things have been great and familiar once more. Different user interface, different command lines. But the passion remained the same.
Linedata has provided me with access to a variety of leading platforms and technologies, including AWS. I had the opportunity to experience labs from both an administrator by network configuration, resource creation and a development standpoint using CSharp and AWS Lambda.

\subsection{Virtualization(VMs), Containerization (Docker)}
Before moving on to containers and Docker, I had a significant amount of fun experimenting with the virtual machine and interacting with the terminal via SSH and RDP. I wrote an article on the subject that delves deeper into these ideas here \href{https://blog.yahya-abulhaj.dev/containers-docker-or-what-exactly-is-that}{blog.yahya-abulhaj.dev/containers-docker-or-what-exactly-is-that}.


\subsection{Infrastructure as code: Terraform and Ansible}

IaC refers to the management and provisioning of infrastructure through the use of code rather than a graphical user interface. The terminal can be used to automate the majority of cloud tasks. As a result, the combination of these technologies is extremely potent.\newline

I also wrote something about this topic because it was relevant to my day job and saved me a lot of time. \href{https://blog.yahya-abulhaj.dev/why-hashicorp-terraform-certification-resources}{blog.yahya-abulhaj.dev/why-hashicorp-terraform-certification-resources
} 