\chapter*{CONCLUSION AND FUTURE CAREER}
\addcontentsline{toc}{chapter}{General Conclusion}

\section{CONCLUSION}

Today's economic crisis affects everyone in the Tunisia, especially young adults who have just graduated from high school and are preparing for a life on their own. So the most important question for any young person is what they want to do with their lives. It is significant because if we make the wrong choices, we will waste our money, our time, and possibly our mental and physical health. However, we may not know whether the path we chose is the right one until later in life. Right now, I am confident in my decision to become a cloud obsessed.


However, in order to ensure the long-term success of Cloud Computing, the chapter addresses some significant challenges that the Cloud paradigm faces. User privacy, data security, data lock-in, availability, disaster recovery, performance, scalability, energy efficiency, and programmability are all issues that must be carefully addressed in future research.

\section{Further Career}
The demand for Cloud Computing professionals is expected to grow exponentially as more and more businesses implement this technology.
I have a strong belief in my vision, and I intend to continue on my path to become the best I can be by utilizing these user-friendly services and adding value to the world. The cloud will undoubtedly provide me with the ability to accomplish things on a large scale.


\begin{flushright}\LARGE
\bf{Thank you for reading.}
\end{flushright}
